Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-11 krs-survey.tex
Improved section on performance evaluation
Introduced several concepts and notation (relaxation time,
scalability...)

Benchmarks of symbolic systems for robots are notoriously hard to conduct for
several reasons: identifying good metrics for robotic experiments in general is
difficult because of the complex interactions between tenth of modules running
in parallel. Isolating the role of one specific component is thus hard.
Furthermore, knowledge representation systems are usually tightly connected to
numerous other modules, and the lack of standard API for knowledge services
makes it especially hard to switch between KRS to compare them. Also, because
service robots are design to act in rich, dynamic environments, possibly with
humans, building repeatable experiments is challenging.

Cognitive architectures and KRS in particular are consequently often
benchmarked with synthetic datasets (which leads to other issues: how to assess
the meaningfulness of the performance of a reasoner on an artificial
ontology?~\cite{Bail2010}) or toy experiments~\cite{Chong2009} that do
not reflect real-world complexity.

While evaluating the performances of knowledge representation systems
themselves may be difficult, the cognitive performances of the robot as a whole
can be also evaluated through ``classical'' tests from the psychology (like
False-Belief experiments~\cite{Leslie2000} or the Token
test~\cite{DiSimoni1978}).

>>>>

Benchmarks of symbolic systems for robots are hard to conduct for
several reasons: identifying good metrics for robotic experiments in general is
difficult because of the complex interactions between tenth of modules running
in parallel, and isolating one specific component is difficult.
Also, knowledge representation systems are often tightly coupled to
the other modules, and the lack of standard API for knowledge services
makes it especially hard to switch between KRS to compare them. Finally, because
service robots are design to act in rich, dynamic environments, possibly with
humans, building repeatable experiments is challenging.

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf D.5 Performance Evaluation}
            child {node {{\bf D.5.2} Cognitive Performances}}
            child {node {{\bf D.5.1} Raw Performances}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

\paragraph{Raw Performances} The \emph{raw performance} is evaluated on
quantitative benchmarks. The main metric is the \emph{scalability}
$\mathcal{S}^{KRS}$ of the system with the size of the knowledge base
$\sigma=|\Delta^{\mathcal{I}}|$  (in term of atoms or statements).

We call \emph{relaxation time} $\mathcal{R}^{\mathcal{M}}$ the (averaged) time
required by the system after a model modification of type $\mathcal{M}$ before
being available for further interaction, and \emph{query time}
$\mathcal{Q}^{\mathcal{M}'}$ the (averaged) time to execute a query of
complexity $\mathcal{M}'$ on the KRS. The type $\mathcal{M}$ of model
alteration is either an ABox modification (addition/removal of an instance) or
a TBox alteration (addition/removal of a class, a class restriction or a rule).
Query complexity $\mathcal{M}'$ is...\fxwarning{find references}.

\emph{Temporal scalability} is defined in term of the nature of the function
$f^{\mathcal{M}, \mathcal{M}'}(\sigma) = \mathcal{R}^{\mathcal{M}}(\sigma) +
\mathcal{Q}^{\mathcal{M}'}(\sigma)$ (\ie the relation of the relaxation time
and query time to the knowledge base size). \emph{Space scalability} is the
relation of memory consumption to the size. The scalability is tightly coupled
to the expressiveness of the underlying knowledge model, which need to be known
for the scalability measurement to be meaningful.

Note that robotic applications may have a knowledge base size relatively small
compared to the complexity of its TBox. In that case the relaxation and query
times for a constant, average knowledge size $\sigma$ may be more relevant as a
metric for KRS raw performance.

Because of coupling and repeatability issues we have mentioned, raw
performances of KRS are often benchmarked with synthetic datasets (which leads
to issues: how to assess the meaningfulness of the performance of a reasoner on
an artificial ontology?~\cite{Bail2010}) or toy experiments~\cite{Chong2009}
that do not always model the whole complexity of real-world application.

\paragraph{Cognitive Performances} While evaluating the raw performances of
knowledge representation systems in a relevant manner may be difficult, the cognitive
performances of the robot as a whole can be also evaluated through
``classical'' tests from the psychology (like False-Belief
experiments~\cite{Leslie2000} or the Token test~\cite{DiSimoni1978}).
